---
title: "Iteration_List_Columns"
author: "Kino Watanabe"
date: "2025-10-28"
output: html_document
---

```{r}
library(tidyverse)
library(rvest)
```

Make a list

```{r}
set.seed(1)

vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)


l = list(
  vec_numeric = 1:8,
  mat         = matrix(1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000)))
l
```
Make a different list

```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )

is.list(list_norms)
```


(copy and paste the function from last time)


```{r}

```

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

* We can apply the mean_and_sd function to each element of `list_norms` using the lines below.

```{r}
mean_and_sd(list_norms[[1]])
mean_and_sd(list_norms[[2]])
mean_and_sd(list_norms[[3]])
mean_and_sd(list_norms[[4]])
```

* tedius --> want to replicate this using `for loop`

Use a loop to iterate!

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norms[[i]])
}

output
```
# use `map` to do the same thing
* `map`

```{r}
output = map(list_norms, mean_and_sd)
output = map(list_norms, median)
```

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = median(list_norms[[i]])
}

output = map(list_norms, median)
```

### `map` variants
```{r}
output = map_dbl(list_norms, median, .id = "sample")
output = map_dfr(list_norms, mean_and_sd, .id = "sample")

```


# LIST COLUMN

Try to put my list into a dataframe. 

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    sample = list_norms
  ) 
```

* both have same legnth = 4, so they will 

Did this really work?
```{r}
listcol_df |> pull(name)
listcol_df |> pull(sample)

```
can i apply `mean_and_sd` ?

```{r}
mean_and_sd(pull(listcol_df, sample)[[1]])
mean_and_sd(pull(listcol_df, sample)[[2]])
mean_and_sd(pull(listcol_df, sample)[[3]])
mean_and_sd(pull(listcol_df, sample)[[4]])
```

iternate using `map`

```{r}
map(pull(listcol_df, sample), mean_and_sd)

```
adding a column

```{r}
listcol_df = 
  listcol_df |> 
  mutate(summary = map(sample, mean_and_sd))

listcol_df

```

```{r}
listcol_df |> 
  select(-sample) |> 
  unnest(summary)
```

# Revisit NDSUH


```{r}
nsduh_table <- function(html, table_num) {
  
  table = 
    html |> 
    html_table() |> 
    nth(table_num) |>
    slice(-1) |> 
    select(-contains("P Value")) |>
    pivot_longer(
      -State,
      names_to = "age_year", 
      values_to = "percent") |>
    separate(age_year, into = c("age", "year"), sep = "\\(") |>
    mutate(
      year = str_replace(year, "\\)", ""),
      percent = str_replace(percent, "[a-c]$", ""),
      percent = as.numeric(percent)) |>
    filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
  
  table
}


```

Try this with a `for` loop

```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)

output = vector("list", 3)

for (i in c(1, 4, 5)) {
  output[[i]] = nsduh_table(nsduh_html, i)
}

nsduh_results = bind_rows(output)
```


Do this with `map`

```{r}

```

Do this all in the data frame.

```{r}
nsduh_results= 
  tibble(
    name = c("marj", "cocaine", "heroine"),
    number = c(1, 4, 5)) |> 
  mutate(table = map(number, nsduh_table, html = nsduh_html)) |> 
  unnest(cols = "table")
```

# look at weather data

```{r}
library(p8105.datasets)
data("weather_df")

weather_nest = 
  nest(weather_df, data = date:tmin)

weather_nest
```

